\newpage
\section{CROWDSALE} \label{crowdsale}

In order to raise funds and kickstart the BlockLicense Ecosystem development, we will be running a crowdfunding campaign during which LCN will be exchanged for ETHER. The campaign will run in two stages over a period of \textit{12 weeks}. As we can see in Table \ref{table:coindistribution}, a total of \textit{700,000,000LCN} will be issued at a price of \textit{2,000LCN per ETH}. During Stage 1 of crowdfunding \textit{5\%} of the total LCN will be made available for purchase, while during Stage 2, \textit{65\%} of the total LCN will be made available. 
\newline
\bigskip
BlockLabs will reserve the remaining \textit{30\%} of the total LCN issued to cover:

\begin{itemize}
\item -- Bounty Tokens
\item -- Crowdsale Bonuses
\item -- Market Liquidity (if needed)
\item -- BlockLicense needs
\end{itemize}

After the end of the crowdsale campaign (Stages 1 \& 2) all unsold LCN from the pool of LCN available during the campaign will be burned and LCN will be listed in several crypto exchanges to be traded at will.
\newline
\bigskip
Funds raised during the crowdsale will be used to cover costs in the following areas:

\begin{itemize}
\item \textbf{Marketing:} - Advertising, press releases, videos, social media etc
\item \textbf{Capital:} - Funds available as working capital for BlockLicense
\item \textbf{Security:} - Security auditing and fortification of payment processing EVM code
\item \textbf{Founders:} - The founders fee
\item \textbf{Legal:} - BlockLicense legal costs
\item \textbf{Sundry:} - Unpredicted expenses associated with product development and launch
\item \textbf{Support:} - Funds provided to external partners
\end{itemize}

In the sections that follow we analyze each crowdfunding stage carefully and show that funds raised serve vital needs of the BlockLicense project.


\begin{table}[t]
\begin{center}
\begin{tabular}{c c c c c}
& & \\ % put some space after the caption
\toprule
\textbf{LCN Issued} & \textbf{ETH Rate} & \textbf{BlockLabs Reserve}  & \textbf{Stage 1: Presale} & \textbf{Stage 2: ICO} \\
\midrule
700,000,000 & 2,000 LCN for 1 ETH & 30\% & 5\% & 65\% \\
\bottomrule
\end{tabular}
\end{center}
\caption{LCN Distribution}
\label{table:coindistribution}
\end{table}



\subsection{Stage 1: Presale}


During this stage we aim to raise funds that will be used to cover initial expenses related to the BlockLicense project. These include vital costs such as security auditing of our smart contract code, marketing \& promotional costs associated with making the BlockLicense project known to a wider audience and supporting Stage 2 of our crowdfunding campaign.


\begin{itemize}
\item --- Any remaining LCN from the Presale stage will be added to the pool of LCN available during Stage 2: ICO.
\item --- In case the project doesn't reach its minimum target, any funds raised during the presale stage are non-refundable. 
\end{itemize}

Presale will run over a period of 4 weeks and bonus LCN will be given to contributors as shown in Table \ref{presale-bonus}:

\begin{table}[h]
\centering
\begin{tabular}{@{}lclll@{}}
\toprule
& \textbf{Week 1} & \multicolumn{1}{c}{\textbf{Week 2}} & \multicolumn{1}{c}{\textbf{Week 3}} & \multicolumn{1}{c}{\textbf{Week 4}} \\ 
\midrule
\multicolumn{1}{r}{\textbf{Bonus}} & 30\%            & 30\%                                & 25\%                                & 25\%   \\ 
\bottomrule
\end{tabular}
\caption{Presale Bonus LCN}
\label{presale-bonus}
\end{table}

The allocation of Ether raised during Presale depends on the total sum raised. The first 100ETH raised will be allocated and used as described in Table \ref{presale-fund-a}. 
\bigskip
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]
\centering
\begin{tabular}{@{}lccccccc@{}}
\toprule
& \textbf{Marketing} & \textbf{Security} & \textbf{Capital} & \textbf{Founders} & \textbf{Legal} & \textbf{Sundry} & \textbf{Support} \\ 
\midrule
\multicolumn{1}{r}{\textbf{Fund Allocation}} & 65\%               & 35\%              & 0\%              & 0\%               & 0\%            & 0\%             & 0\%              \\ 
\bottomrule
\end{tabular}
\caption{Allocation of Presale funds for the first 100ETH raised}
\label{presale-fund-a}
\end{table}

\bigskip
Any Ether raised during Presale above the sum of 100 ETH will be allocated and used as described in Table \ref{presale-fund-b}: 
\begin{table}[h]
\centering
\begin{tabular}{@{}lccccccc@{}}
\toprule
& \textbf{Marketing} & \textbf{Security} & \textbf{Capital} & \textbf{Founders} & \textbf{Legal} & \textbf{Sundry} & \textbf{Support} \\ 
\midrule
\multicolumn{1}{r}{\textbf{Fund Allocation}} & 55\%               & 10\%              & 20\%              & 10\%               & 2\%            & 1\%             & 2\%              \\ 
\bottomrule
\end{tabular}
\caption{Allocation of Presale funds raised above 100ETH }
\label{presale-fund-b}
\end{table}

\newpage

\subsection{Stage 2: ICO}
This is the main stage of our crowdfunding campaign that will determine the fate of the BlockLicense project.

ICO will run over a period of 6 weeks and bonus coins will be distributed as described in Table \ref{ico-bonus}:


\begin{table}[h]
\centering
\begin{tabular}{@{}lllllll@{}}
\toprule
               & \textbf{Week 1}          & \textbf{Week 2}          & \textbf{Week 3}          & \textbf{Week 4}          & \textbf{Week 5}          & \textbf{Week 6}          \\ \midrule
\textbf{Bonus} & \multicolumn{1}{c}{20\%} & \multicolumn{1}{c}{20\%} & \multicolumn{1}{c}{15\%} & \multicolumn{1}{c}{15\%} & \multicolumn{1}{c}{15\%} & \multicolumn{1}{c}{15\%} \\ \bottomrule
\end{tabular}
\caption{ICO Bonus LCN}
\label{ico-bonus}
\end{table}

\bigskip

Funds raised during the ICO will be allocated as described in Table \ref{ico-fund}:
\begin{table}[h]
\centering
\begin{tabular}{@{}lccccccc@{}}
\toprule
& \textbf{Marketing} & \textbf{Security} & \textbf{Capital} & \textbf{Founders} & \textbf{Legal} & \textbf{Sundry} & \textbf{Support} \\ 
\midrule
\multicolumn{1}{r}{\textbf{Fund Allocation}} & 30\%               & 1\%              & 40\%              & 25\%               & 1\%            & 2\%             & 1\%              \\ 
\bottomrule
\end{tabular}
\caption{Allocation of ICO funds }
\label{ico-fund}
\end{table}



\subsection{Minimum Goals}

The sustainability of the BlockLicense project depends on the amount of ETH that will be raised during the crowdsale campaign. A high enough sum guarantees that there are enough funds to create the BlockLicense Ecosystem in its entirety, while a low sum will prevent the project from continuing. In the latter case, funds raised during Stage 2 will be refundable, while funds raised during Stage 1 will be non-refundable. 

\begin{multicols}{2}
\begin{equation} \label{eq:goalA}
  \operatorname{MinGoalA} =
  \begin{cases}
    1,000\operatorname{ETH} & \text{if 1 ETH $\geq$ \$250} \\
     2,000\operatorname{ETH} & \text{otherwise}
  \end{cases}
\end{equation}\break
\begin{equation} \label{eq:goalB}
  \operatorname{MinGoalB} =
  \begin{cases}
    5,000\operatorname{ETH} & \text{if 1 ETH $\geq$ \$250} \\
     10,000\operatorname{ETH} & \text{otherwise}
  \end{cases}
\end{equation}
\end{multicols}



There are two minimum crowdfunding goals that we have set for BlockLicense, namely MinGoalA (\ref{eq:goalA}) and MinGoalB (\ref{eq:goalB}). If MinGoalA fails, the project will not continue. If MinGoalA succeeds while MinGoalB fails, we will use raised funds to build the Desktop Application. If MinGoalB succeeds, we will use raised funds to create the entire Ecosystem.