\newpage
\section{TEAM} \label{team}
\bigskip
\noindent
\textbf{Nikolas Psaroudakis} \newline
\medskip Founder, Technical Director
\newline
Nikolas is a multidisciplinary developer and maker. Driven by his innate curiosity, he enjoys finding out how things work. He views code as an expressive medium and excels in producing technological solutions for forward looking businesses and individuals. He has been educated in two continents and has lived and worked in four countries. He holds a BSc in Physics, an MSc in the area of Computer Vision and an MPS in Interactive Telecommunications. Nikolas is a firm believer in the potential of the decentralized web as an agent for change and the positive impact blockchain \& Web 3.0 can have on the society as a whole.\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Katerina Stavraki}\newline
\medskip Cofounder, Business Director
\newline
Katerina is a multi-skilled corporate mind with over 15 years of experience in B2B and B2C multinational corporations. She holds a BEng in Communications Engineering and an MSc in Electrical Power Engineering and Management from top institutions in the UK. Katerina is effective and efficient and believes in TRN, short for Technology-Resolution-Now. Her unique project management skills gained her experience in diverse fields such as business development and planning as well as strategic projects across several countries in the world. Katerina is a blockchain enthusiast \& investor and believes in technological revolution behind the numbers.\par


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Yiannis Koutsoupas}\newline
\medskip Cofounder, Art Director
\newline
Yiannis is a designer at heart and practice, a problem solver and UX/UI expert; his experience spans from websites to apps since 2000. Yannis’s portfolio of collaborators includes agencies, global corporations \& innovative startups among others. His creative portfolio holds innovative projects, nominated and award winning projects in the realms of broadcasting, advertising and disruptive technological programs.
 \par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Theodore Moulos}\newline
\medskip Cofounder, Growth Strategist
\newline
Theodore is a Growth-Hacking Strategist. He has been on the game for over 15 years during which he has won over intrapreneurship and entrepreneurship. Having conquered all types of positions (CEO, COO, BoD member, etc.) within international companies (e.g. Pinnatta App) he now goes by ‘Theodore’ and during his free time, he coaches startups. He is the owner of GrowthRocks and Viral-Loops companies, taming digital marketing practices.
\par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Jason Kritikos}\newline
\medskip iOS \& Backend Developer
\newline
Jason is an iOS addict and a restless coder. Holding a BSc in Computer Science and a master’s degree in mobile \& wireless networks, Jason has proven early his passion for anything mobile. Having worked in London and Athens for more than 15 years, he’s gained significant experience in building anything from backend systems to mobile apps for both large corporations and innovative startups. He enjoys spinning records and shooting with his camera.
\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Alex Galinos}\newline
\medskip Business Advisor
\newline 
Alex is a Harvard Business School graduate determined to offer experience and expertise to his country. More specifically by holding, throughout his career, managing positions in the Hellenic Ministry of Foreign Affairs, the Athens Development and Destination Management Agency and the Athens City Hall. As a professional, Alex is a firm believer and, thus, invests in business extroversion and openness.
\par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Konstantina Chardalia}\newline
\medskip Financial Advisor
\newline
Konstantina is a finance mastermind using her devotion to numbers and her loyalty to forecasting and planning for the greater balance. She graduated from top universities in Greece and the UK and established herself as a professional expert in Greece. Konstantina’s experience in multinational corporations and her consistency in growing and evolving make her a uniquely gifted partner.
\par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Sofia Stavraki}\newline
\medskip Legal Advisor
\newline
Sofia is a Supreme Court lawyer. She is a Democritus University of Thrace Alumna who practices Criminal \& Trade Law, Civil Law and issues Legal agreements from her private law firm/office of 2 branches, in Lamia and Athens, Greece, owned since 2002 \& 2011 accordingly. Sofia is an avid writer and reader manifested in her rich professional website, in her published law essays and her 500+ wins in Greek courts until today.
\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
\textbf{Olga Kachramanoglou}\newline
\medskip Copywriter \& Social Media 
\newline
Olga is a loyal writer. She identifies herself as an anthropologist but writing is her moneymaker. From advertising copywriter-before the digital Big Bang-to content creator she never stops to write for the digital market (SEO, social media \& blogging) and for fun. She was once labeled handicap for her wild imagination in writing. However, she is, still, fully functional and social but would rather write to you than speak to you.
 \par